\def\year{2026}\relax

\documentclass[letterpaper]{article} % DO NOT CHANGE THIS
\usepackage{aaai25}  % DO NOT CHANGE THIS
\usepackage{times}  % DO NOT CHANGE THIS
\usepackage{helvet}  % DO NOT CHANGE THIS
\usepackage{courier}  % DO NOT CHANGE THIS
\usepackage[hyphens]{url}  % DO NOT CHANGE THIS
\usepackage{graphicx} % DO NOT CHANGE THIS
\urlstyle{rm} % DO NOT CHANGE THIS
\def\UrlFont{\rm}  % DO NOT CHANGE THIS
\usepackage{natbib}  % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
\usepackage{caption} % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
\DeclareCaptionStyle{ruled}{labelfont=normalfont,labelsep=colon,strut=off} % DO NOT CHANGE THIS
\frenchspacing  % DO NOT CHANGE THIS
\setlength{\pdfpagewidth}{8.5in}  % DO NOT CHANGE THIS
\setlength{\pdfpageheight}{11in}  % DO NOT CHANGE THIS
%
% These are recommended to typeset algorithms but not required. See the subsubsection on algorithms. Remove them if you don't have algorithms in your paper.
\usepackage{algorithm}
\usepackage{algorithmic}

% Checklist macros
\usepackage{xcolor}
\newcommand{\answerYes}[1]{\textcolor{blue}{#1}} 
\newcommand{\answerNo}[1]{\textcolor{teal}{#1}} 
\newcommand{\answerNA}[1]{\textcolor{gray}{#1}} 
\newcommand{\answerTODO}[1]{\textcolor{red}{#1}} 
%
% These are recommended to typeset listings but not required. See the subsubsection on listing. Remove this block if you don't have listings in your paper.
\usepackage{newfloat}
\usepackage{listings}
\lstset{%
	basicstyle={\footnotesize\ttfamily},% footnotesize acceptable for monospace
	numbers=left,numberstyle=\footnotesize,xleftmargin=2em,% show line numbers, remove this entire line if you don't want the numbers.
	aboveskip=0pt,belowskip=0pt,%
	showstringspaces=false,tabsize=2,breaklines=true}
\floatstyle{ruled}
\newfloat{listing}{tb}{lst}{}
\floatname{listing}{Listing}
%
%\nocopyright
%
% PDF Info Is REQUIRED.
% For /Title, write your title in Mixed Case.
% Don't use accents or commands. Retain the parentheses.
% For /Author, add all authors within the parentheses,
% separated by commas. No accents, special characters
% or commands are allowed.
% Keep the /TemplateVersion tag as is
\pdfinfo{
/Title (AAAI ICWSM Paper Checklist)
/Author (AAAI ICWSM 2026 Organizing Committee)
/TemplateVersion (2024.8)
}

\setcounter{secnumdepth}{0} %May be changed to 1 or 2 if section numbers are desired.

% The file aaai22.sty is the style file for AAAI Press
% proceedings, working notes, and technical reports.
%

% Title

% Your title must be in mixed case, not sentence case.
% That means all verbs (including short verbs like be, is, using,and go),
% nouns, adverbs, adjectives should be capitalized, including both words in hyphenated terms, while
% articles, conjunctions, and prepositions are lower case unless they
% directly follow a colon or long dash
\title{AAAI ICWSM Paper Checklist}
\author{
    %Authors
    % All authors must be in the same font size and format.
    Written by the AAAI ICWSM 2025 Organizing Committee}
\affiliations{
    % email address must be in roman text type, not monospace or sans serif
    pc.chairs@icwsm.org
%
% See more examples next
}


\begin{document}

\maketitle

\begin{abstract}
This document offers a Paper Checklist to be appended at the end of all submissions to rounds of the AAAI ICWSM conference. 
\end{abstract}

\section{Overview}

This document offers a checklist to append at the end of a AAAI ICWSM 2026 submission. The paper checklist has been adapted from the NeurIPS 2023 guidelines~\citep{neurips}, the Natural Language Processing (NLP) reviewing checklist compiled by~\citet{benotti2023understanding}, and the consensus-based transparency checklist~\citep{aczel2020consensus}. The checklist follows the references.  While addressing these questions in the body of their manuscript, authors can explore the discussions provided in prior work~\citep{neurips,aczel2020consensus,benotti2023understanding,ashurst2020guide,gebru2021datasheets} as a starting point. The ethics reading list\footnote{https://github.com/acl-org/ethics-reading-list} compiled by~\citet{benotti2023understanding} provides examples of papers discussing ethical considerations in NLP research.

\subsection{Detailed Instructions}
Please do not inadvertently compromise the anonymity of your submission; you are allowed to be vague, within reason, regarding institutional affiliations. 

Please do not modify the questions and only use the provided macros for your answers. In your paper, please delete all text in the \textbf{Overview} and \textbf{Detailed Instructions} sections, as well as all subsection headers, keeping only the \textbf{Checklist} section heading above along with the questions/answers below. 

For each question, change the default \answerTODO{Answer} to \answerYes{Yes, and},
\answerNo{No, because}, or \answerNA{NA}, when the question seems inappropriate for your research study. You are strongly encouraged to include a {\bf
justification to your answer}, either by referencing the appropriate section of your paper or providing a brief inline description. Within the Checklist section, you may supplement your answers with a brief discussion that expands on answers to the checklist where necessary. For example:
\begin{itemize}
  \item Did you include the license to the code and datasets? \answerYes{Yes, see the Methods and the Appendix.}
  \item Did you include the license to the code and datasets? \answerNo{No, because the code and the data are proprietary.}
  \item Did you include the license to the code and datasets? \answerNA{NA}
\end{itemize}
%%% END INSTRUCTIONS %%%

\subsection{Paper Checklist to be included in your paper}

\begin{enumerate}

\item For most authors...
\begin{enumerate}
    \item  Would answering this research question advance science without violating social contracts, such as violating privacy norms, perpetuating unfair profiling, exacerbating the socio-economic divide, or implying disrespect to societies or cultures?
    \answerTODO{Answer}
  \item Do your main claims in the abstract and introduction accurately reflect the paper's contributions and scope?
    \answerTODO{Answer}
   \item Do you clarify how the proposed methodological approach is appropriate for the claims made? 
    \answerTODO{Answer}
   \item Do you clarify what are possible artifacts in the data used, given population-specific distributions?
    \answerTODO{Answer}
  \item Did you describe the limitations of your work?
    \answerTODO{Answer}
  \item Did you discuss any potential negative societal impacts of your work?
    \answerTODO{Answer}
      \item Did you discuss any potential misuse of your work?
    \answerTODO{Answer}
    \item Did you describe steps taken to prevent or mitigate potential negative outcomes of the research, such as data and model documentation, data anonymization, responsible release, access control, and the reproducibility of findings?
    \answerTODO{Answer}
  \item Have you read the ethics review guidelines and ensured that your paper conforms to them?
    \answerTODO{Answer}
\end{enumerate}

\item Additionally, if your study involves hypotheses testing...
\begin{enumerate}
  \item Did you clearly state the assumptions underlying all theoretical results?
    \answerTODO{Answer}
  \item Have you provided justifications for all theoretical results?
    \answerTODO{Answer}
  \item Did you discuss competing hypotheses or theories that might challenge or complement your theoretical results?
    \answerTODO{Answer}
  \item Have you considered alternative mechanisms or explanations that might account for the same outcomes observed in your study?
    \answerTODO{Answer}
  \item Did you address potential biases or limitations in your theoretical framework?
    \answerTODO{Answer}
  \item Have you related your theoretical results to the existing literature in social science?
    \answerTODO{Answer}
  \item Did you discuss the implications of your theoretical results for policy, practice, or further research in the social science domain?
    \answerTODO{Answer}
\end{enumerate}

\item Additionally, if you are including theoretical proofs...
\begin{enumerate}
  \item Did you state the full set of assumptions of all theoretical results?
    \answerTODO{Answer}
	\item Did you include complete proofs of all theoretical results?
    \answerTODO{Answer}
\end{enumerate}

\item Additionally, if you ran machine learning experiments...
\begin{enumerate}
  \item Did you include the code, data, and instructions needed to reproduce the main experimental results (either in the supplemental material or as a URL)?
    \answerTODO{Answer}
  \item Did you specify all the training details (e.g., data splits, hyperparameters, how they were chosen)?
    \answerTODO{Answer}
     \item Did you report error bars (e.g., with respect to the random seed after running experiments multiple times)?
    \answerTODO{Answer}
	\item Did you include the total amount of compute and the type of resources used (e.g., type of GPUs, internal cluster, or cloud provider)?
    \answerTODO{Answer}
     \item Do you justify how the proposed evaluation is sufficient and appropriate to the claims made? 
    \answerTODO{Answer}
     \item Do you discuss what is ``the cost`` of misclassification and fault (in)tolerance?
    \answerTODO{Answer}
  
\end{enumerate}

\item Additionally, if you are using existing assets (e.g., code, data, models) or curating/releasing new assets, \textbf{without compromising anonymity}...
\begin{enumerate}
  \item If your work uses existing assets, did you cite the creators?
    \answerTODO{Answer}
  \item Did you mention the license of the assets?
    \answerTODO{Answer}
  \item Did you include any new assets in the supplemental material or as a URL?
    \answerTODO{Answer}
  \item Did you discuss whether and how consent was obtained from people whose data you're using/curating?
    \answerTODO{Answer}
  \item Did you discuss whether the data you are using/curating contains personally identifiable information or offensive content?
    \answerTODO{Answer}
\item If you are curating or releasing new datasets, did you discuss how you intend to make your datasets FAIR (see \citet{fair})?
\answerTODO{Answer}
\item If you are curating or releasing new datasets, did you create a Datasheet for the Dataset (see \citet{gebru2021datasheets})? 
\answerTODO{Answer}
\end{enumerate}

\item Additionally, if you used crowdsourcing or conducted research with human subjects, \textbf{without compromising anonymity}...
\begin{enumerate}
  \item Did you include the full text of instructions given to participants and screenshots?
    \answerTODO{Answer}
  \item Did you describe any potential participant risks, with mentions of Institutional Review Board (IRB) approvals?
    \answerTODO{Answer}
  \item Did you include the estimated hourly wage paid to participants and the total amount spent on participant compensation?
    \answerTODO{Answer}
   \item Did you discuss how data is stored, shared, and deidentified?
   \answerTODO{Answer}
\end{enumerate}

\end{enumerate}


\bibliography{aaai25}

\end{document}
