% Main LaTeX file - ICWSM 2025 Paper
% Based on official AAAI/ICWSM template
\documentclass[letterpaper]{article} % DO NOT CHANGE THIS
\usepackage[submission]{aaai25}  % DO NOT CHANGE THIS (use submission for anonymous)
\usepackage{times}  % DO NOT CHANGE THIS
\usepackage{helvet}  % DO NOT CHANGE THIS
\usepackage{courier}  % DO NOT CHANGE THIS
\usepackage[hyphens]{url}  % DO NOT CHANGE THIS
\usepackage{graphicx} % DO NOT CHANGE THIS
\urlstyle{rm} % DO NOT CHANGE THIS
\def\UrlFont{\rm}  % DO NOT CHANGE THIS
\usepackage{natbib}  % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
\usepackage{caption} % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
\frenchspacing  % DO NOT CHANGE THIS
\setlength{\pdfpagewidth}{8.5in} % DO NOT CHANGE THIS
\setlength{\pdfpageheight}{11in} % DO NOT CHANGE THIS

% Additional allowed packages
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}

% Checklist macros
\newcommand{\answerYes}[1]{\textcolor{blue}{#1}} 
\newcommand{\answerNo}[1]{\textcolor{teal}{#1}} 
\newcommand{\answerNA}[1]{\textcolor{gray}{#1}} 
\newcommand{\answerTODO}[1]{\textcolor{red}{#1}} 

% PDF Info
\pdfinfo{
/Title (Summit Diplomacy and Social Media Framing)
/Author (Anonymous Submission)
/TemplateVersion (2025.1)
}

\setcounter{secnumdepth}{0} % No section numbers

% Title - Must be in Title Case
\title{Summit Diplomacy and Social Media Framing: \\
A Causal Analysis of U.S.-North Korea Summits on Reddit Public Opinion}

% For anonymous submission
\author{
    Anonymous Submission
}
\affiliations{
    
}

% For camera-ready (uncomment and fill in):
% \author{
%     Jun Sin\textsuperscript{\rm 1}
% }
% \affiliations{
%     \textsuperscript{\rm 1}University of Texas at Austin\\
%     Austin, TX, USA\\
%     jun.sin@utexas.edu
% }

\begin{document}

\maketitle

\begin{abstract}
\input{sections/abstract}
\end{abstract}

% Optional: Links to code/data (uncomment for camera-ready)
% \begin{links}
%     \link{Code}{https://github.com/...}
%     \link{Datasets}{https://...}
% \end{links}

% Main sections
\input{sections/introduction}
\input{sections/related_work}
\input{sections/data}
\input{sections/method}
\input{sections/results}
\input{sections/discussion}
\input{sections/conclusion}

% Acknowledgments (uncomment for camera-ready)
% \section*{Acknowledgments}
% We thank...

% References
\bibliography{references}

% Paper Checklist (Required for ICWSM submission)
\newpage
\section*{Paper Checklist}

\begin{enumerate}

\item For most authors...
\begin{enumerate}
    \item Would answering this research question advance science without violating social contracts?
    \answerYes{Yes, this study examines public discourse and does not involve private data.}
    
    \item Do your main claims accurately reflect the paper's contributions?
    \answerYes{Yes, see Abstract and Section 1.}
    
    \item Do you clarify how the proposed methodological approach is appropriate?
    \answerYes{Yes, see Section 4 (Method) for DID justification.}
    
    \item Do you clarify what are possible artifacts in the data?
    \answerYes{Yes, we discuss platform-specific limitations in Section 6.}
    
    \item Did you describe the limitations of your work?
    \answerYes{Yes, see Section 6 (Discussion - Limitations).}
    
    \item Did you discuss potential negative societal impacts?
    \answerNA{NA, this is observational research on public discourse.}
    
    \item Did you discuss potential misuse of your work?
    \answerNA{NA, findings describe public opinion patterns.}
    
    \item Did you describe steps to prevent negative outcomes?
    \answerYes{Yes, we use aggregated data and do not identify individuals.}
    
    \item Have you ensured your paper conforms to ethics guidelines?
    \answerYes{Yes.}
\end{enumerate}

\item Additionally, if your study involves hypothesis testing...
\begin{enumerate}
    \item Did you clearly state assumptions?
    \answerYes{Yes, parallel trends assumption in Section 4 and 5.}
    
    \item Have you provided justifications for theoretical results?
    \answerYes{Yes, we validate assumptions empirically.}
    
    \item Did you discuss competing hypotheses?
    \answerYes{Yes, we use multiple control groups for robustness.}
    
    \item Have you considered alternative explanations?
    \answerYes{Yes, discussed in Section 6.}
    
    \item Did you address potential biases?
    \answerYes{Yes, see Limitations in Section 6.}
    
    \item Have you related results to existing literature?
    \answerYes{Yes, see Section 2 (Related Work).}
    
    \item Did you discuss implications?
    \answerYes{Yes, see Section 6 (Discussion).}
\end{enumerate}

\item Additionally, if you ran machine learning experiments...
\begin{enumerate}
    \item Did you include code and data?
    \answerTODO{Will be provided upon acceptance.}
    
    \item Did you specify training details?
    \answerYes{Yes, we specify LLM model and prompts in Section 4.}
    
    \item Did you report error bars?
    \answerYes{Yes, standard errors provided in DID tables.}
    
    \item Did you include compute resources?
    \answerYes{GPT-4o-mini API, RoBERTa on local GPU.}
    
    \item Do you justify evaluation appropriateness?
    \answerYes{Yes, we validate LLM against human experts.}
    
    \item Did you discuss misclassification costs?
    \answerYes{Yes, see validation agreement metrics.}
\end{enumerate}

\item Additionally, if using existing assets...
\begin{enumerate}
    \item Did you cite the creators?
    \answerYes{Yes, Arctic Shift API and model citations included.}
    
    \item Did you mention licenses?
    \answerYes{Reddit data via public API; models via standard licenses.}
    
    \item Did you include new assets?
    \answerTODO{Will provide framing-annotated dataset.}
    
    \item Did you discuss consent?
    \answerYes{Reddit posts are public; no identifiable information used.}
    
    \item Does data contain PII?
    \answerNo{No, we use only public posts with anonymized usernames.}
\end{enumerate}

\item Additionally, if you used crowdsourcing or human subjects...
\begin{enumerate}
    \item Did you include instructions?
    \answerYes{Yes, annotation guidelines described in Section 4.}
    
    \item Did you describe participant risks?
    \answerNA{NA, annotators are expert collaborators, not research subjects.}
    
    \item Did you include hourly wage?
    \answerNA{NA, annotators are collaborating researchers.}
    
    \item Did you discuss data storage?
    \answerYes{Annotations stored locally.}
\end{enumerate}

\end{enumerate}

\end{document}
